Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-15 paper.qmd
Updated the package installation by replacing with tidyverse
Try to remove the packages thatdon't want

packages_to_check <- c("remotes", "tibble", "dplyr", "ggplot2", "tidyr", "readr", "patchwork", "colorspace", "kableExtra", "conflicted")

@@

These `R` packages were used for the work: `tidyverse` (@hadley2019), `png` (@simon2022), `Rtsne` (@jesse2015), `umap` (@tomasz2023), `ggplot2` (@hadley2016), `patchwork` (@thomas2024), `colorspace` (@achim2020), `langevitour` (@harisson2024), `conflicted` (@hadley2023), `reticulate` (@kevin2024), `kableExtra` (@hao2024). These `python` packages were used for the work: `trimap` (@amid2022) and `pacmap` (@yingfan2021). The article was created with `R` packages `rticles` (@jjallaire2024), `knitr` (@yihui2014), and `rmarkdown` (@yihui2020). The project's GitHub repository ([https://github.com/JayaniLakshika/paper-nldr-vis-algorithm](https://github.com/JayaniLakshika/paper-nldr-vis-algorithm)) contains all materials required to reproduce this article.

>>>>

packages_to_check <- c("remotes", "tidyverse", "patchwork", "colorspace", "kableExtra", "conflicted")

@@

These `R` packages were used for the work: `tidyverse` (@hadley2019), `Rtsne` (@jesse2015), `umap` (@tomasz2023), `patchwork` (@thomas2024), `colorspace` (@achim2020), `langevitour` (@harisson2024), `conflicted` (@hadley2023), `reticulate` (@kevin2024), `kableExtra` (@hao2024). These `python` packages were used for the work: `trimap` (@amid2022) and `pacmap` (@yingfan2021). The article was created with `R` packages `rticles` (@jjallaire2024), `knitr` (@yihui2014), and `rmarkdown` (@yihui2020). The project's GitHub repository ([https://github.com/JayaniLakshika/paper-nldr-vis-algorithm](https://github.com/JayaniLakshika/paper-nldr-vis-algorithm)) contains all materials required to reproduce this article.
